{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-14 bmvc_review.tex
Comments to table 1 added - figures squeezed

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:OTB100_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123.eps}}
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with those of the
  state-of-the-art tracking algorithms on the UAV123 dataset.}
\label{fig:UAV123_DATASET}
\end{figure}
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_OTB100.eps}}
\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_OTB100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with those of the
  state-of-the-art tracking algorithms on the OTB100 dataset.}
\label{fig:OTB100_DATASET}
\end{figure}

\begin{table}
\smaller
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
\hline\hline
Pr. ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 52.14 & &  \\
SR ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 38.51 & & \\
FPS & 416 & 370 & 425  & 151 & & \\
\hline
\end{tabular}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF. The KCFs highlighted in LCT are applied in every frame as proposed in
\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison. In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).} 
\end{table}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Precision_UAV123_10fps.eps}}
\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123_10fps.eps}}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

>>>>

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker and run $R_{t}^{L}$, $R_{t}^{s}$, and $R_{s}$ in every frame in the given order. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
\hline\hline
Pr. ($20$px) & \color{red} 53.9 & 48.09 & 52.50 & & 52.14 & \textbf{58.16} \\
SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & & 38.51 & \textbf{41.58} \\
FPS & \color{red} 416 & 370 & \textbf{425}  & & 151 & 99 \\
\hline
\end{tabular}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The 2nd method removes $R_{t}^{S}$ (fig.~\ref{Workflows}) and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$. We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF. The KCFs highlighted in LCT are applied in every frame in the listed order as proposed in
\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison. In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).} 
\label{table:Comparison_to_LCT}
\end{table}

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_OTB100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_OTB100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with those of the
  state-of-the-art tracking algorithms on the UAV123 dataset.}
\label{fig:UAV123_DATASET}
\end{figure}
%\begin{figure}[!h]
%\centering
%\begin{tabular}{ccc}
%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
%\end{tabular}
%\caption{Comparison of {\it E}nKCF's performance with those of the
%  state-of-the-art tracking algorithms on the OTB100 dataset.}
%\label{fig:OTB100_DATASET}
%\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Precision_UAV123_10fps.eps}}
\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Success_UAV123_10fps.eps}}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
